---
title: "Atopic dermatitis and mental-health outcomes — living evidence summary"
subtitle: "Random-effects meta-analysis, monthly-updating"
author: "Review team (TBD)"
date: today
last-updated: today
---

```{r}
#| label: setup
#| echo: false
#| message: false
#| warning: false
suppressPackageStartupMessages({
  library(dplyr); library(readr); library(knitr); library(stringr)
})
gen <- "_generated"
pooled <- read_csv(file.path(gen, "pooled_summary.csv"), show_col_types = FALSE)
grade  <- read_csv(file.path(gen, "grade_draft.csv"),  show_col_types = FALSE)
seed_banner <- file.exists("../data/seed_studies.csv") &&
  identical(Sys.getenv("REVIEW_DATA", "seed_studies.csv"), "seed_studies.csv")
```

::: {.callout-warning}
**This site is currently rendered against the synthetic seed dataset.**
All numbers below are placeholders for pipeline validation. Treat them as
plumbing checks, not evidence.
:::

## What this is

A *living* systematic review and meta-analysis of the association between
adult atopic dermatitis (AD) and three pre-specified mental-health outcomes:
**depression**, **anxiety**, and **suicidality / self-harm**. Pre-registered
on PROSPERO and reported per PRISMA 2020.

## Headline pooled estimates

```{r}
#| label: pooled-table
#| echo: false
pooled |>
  transmute(
    Outcome = stringr::str_to_title(outcome),
    `k studies` = k,
    `Pooled OR` = sprintf("%.2f", pooled_OR),
    `95% CI` = sprintf("%.2f – %.2f", ci_lo, ci_hi),
    `95% PI` = sprintf("%.2f – %.2f", pi_lo, pi_hi),
    `I²` = sprintf("%.0f%%", I2),
    `τ²` = sprintf("%.3f", tau2)) |>
  kable(align = "lrrrrr")
```

## Certainty (draft GRADE)

```{r}
#| label: grade-table
#| echo: false
grade |>
  transmute(
    Outcome = stringr::str_to_title(outcome),
    Starting = starting,
    `Down: RoB` = rob_downgrade,
    `Down: Heterogeneity` = inconsistency_downgrade,
    `Down: Imprecision` = imprecision_downgrade,
    `Down: Pub bias` = pubbias_downgrade,
    `Up: large effect` = upgrade_large_effect,
    Certainty = certainty) |>
  kable(align = "llrrrrrl")
```

## How this updates

A scheduled GitHub Action re-runs the PubMed and Embase queries on the **1st
of every month** (UTC), deduplicates against the corpus, opens a screening
issue for any new candidate records, and — once the team merges newly
extracted rows — re-pools the meta-analyses and re-renders this site.

The full audit trail lives in `search/update_log.md`.
